---
title: "Powerplant Finding Faileurs"
author: "Daniel Lundstrom"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

Here we identify low power outputs, attempt to predict low power times given recent power reading of an inverter,
and do some investigation of correlations of inverter low power performance between different inverters.
Our findings suggest that some inverters are highly correlating, so that they give low power readings together.
Findings also suggest that low power performance for an inverter cannot be predicted by recent power readings.

```{r covariance matrix}
p1.f = p1nz

# create labels for easy reading o correlation table

p1.f$a.res = rep(0,length(p1.f$DAY))
p1.f$b.res = rep(0,length(p1.f$DAY))
p1.f$c.res = rep(0,length(p1.f$DAY))
p1.f$d.res = rep(0,length(p1.f$DAY))
p1.f$e.res = rep(0,length(p1.f$DAY))
p1.f$f.res = rep(0,length(p1.f$DAY))
p1.f$g.res = rep(0,length(p1.f$DAY))
p1.f$h.res = rep(0,length(p1.f$DAY))
p1.f$i.res = rep(0,length(p1.f$DAY))
p1.f$j.res = rep(0,length(p1.f$DAY))
p1.f$k.res = rep(0,length(p1.f$DAY))
p1.f$l.res = rep(0,length(p1.f$DAY))
p1.f$m.res = rep(0,length(p1.f$DAY))
p1.f$n.res = rep(0,length(p1.f$DAY))
p1.f$o.res = rep(0,length(p1.f$DAY))
p1.f$p.res = rep(0,length(p1.f$DAY))
p1.f$q.res = rep(0,length(p1.f$DAY))
p1.f$r.res = rep(0,length(p1.f$DAY))
p1.f$s.res = rep(0,length(p1.f$DAY))
p1.f$t.res = rep(0,length(p1.f$DAY))
p1.f$u.res = rep(0,length(p1.f$DAY))
p1.f$v.res = rep(0,length(p1.f$DAY))

# for each inverter, get residuals of performance from prediction (residual = performance - prediction)
  for (i in 1:22){
    data = p1nz[,1:5];
    data$DC_POWER = p1nz[,i+5];          
    mod=lm(DC_POWER~poly(IRRADIATION,2)+AMBIENT_TEMPERATURE,data=data);
    p1.f[,27+i] = data$DC_POWER - predict(mod,data);
  }

# calculate correlations to find if different inverters generally over/under perform together.
  p1.f = p1.f[,28:49];
  cor(p1.f, y=p1.f, use="all.obs")
  
#generally positive correlation. Some are highly correlated (e.g. a & i), while some are uncorrelated (e.g. f & m).

```

```{r multiple source faileur}

# Identify times when an inverter gives low power yield based on irradiation measurements.
# check to see if this happens on particular days, times of day, irradiation measures,
# or ambient temp measurements.

# low power generally happens around mid to high temp, with most happening at mid temp.
# low power days are sporadic and vary wildly. Sometimes 0 low-power instances occur, sometimes 40, in a day
# low power occurs in a roughly bell-shaped curve, with abnormally high spikes at times (roughly) 590, 650, and 830
# low power occurs in relation to irradiation in a roughly bell-shaped curve, with the center at 0.7 irraiation
# simultaneous low-power from multiple inverters roughly occurs in 2s and 3s

low.day = NULL;
low.time = NULL;
low.pow = NULL;

low.pow.time = NULL;
low.pow.temp = NULL;
low.pow.fail.pairs = NULL;
low.pow.day = NULL;
low.pow.irradiation = NULL;

p1.f = p1

p1.f$numfail = rep(0,length(p1.f$DAY))
p1.f$afail = rep(0,length(p1.f$DAY))
p1.f$bfail = rep(0,length(p1.f$DAY))
p1.f$cfail = rep(0,length(p1.f$DAY))
p1.f$dfail = rep(0,length(p1.f$DAY))
p1.f$efail = rep(0,length(p1.f$DAY))
p1.f$ffail = rep(0,length(p1.f$DAY))
p1.f$gfail = rep(0,length(p1.f$DAY))
p1.f$hfail = rep(0,length(p1.f$DAY))
p1.f$ifail = rep(0,length(p1.f$DAY))
p1.f$jfail = rep(0,length(p1.f$DAY))
p1.f$kfail = rep(0,length(p1.f$DAY))
p1.f$lfail = rep(0,length(p1.f$DAY))
p1.f$mfail = rep(0,length(p1.f$DAY))
p1.f$nfail = rep(0,length(p1.f$DAY))
p1.f$ofail = rep(0,length(p1.f$DAY))
p1.f$pfail = rep(0,length(p1.f$DAY))
p1.f$qfail = rep(0,length(p1.f$DAY))
p1.f$rfail = rep(0,length(p1.f$DAY))
p1.f$sfail = rep(0,length(p1.f$DAY))
p1.f$tfail = rep(0,length(p1.f$DAY))
p1.f$ufail = rep(0,length(p1.f$DAY))
p1.f$vfail = rep(0,length(p1.f$DAY))

for (i in 1:22){
  
  data = p1[,1:5];
  data$DC_POWER = p1[,i+5] 
  z.pow = data$DC_POWER==0;
  mod=lm(DC_POWER~poly(IRRADIATION,2)+AMBIENT_TEMPERATURE,data=data[!z.pow,]);
  variance = var(data$DC_POWER[!z.pow]-predict(mod,data[!z.pow,]));
  sd = sqrt(variance);
  low.pow = !z.pow & data$DC_POWER < (predict(mod,data)-3*sd)
  p1.f$numfail[low.pow] <- p1.f$numfail[low.pow] + 1;
  p1.f[low.pow,28+i] = p1.f[low.pow,28+i] + 1;
  
  
  low.pow.time = c(low.pow.time, data$TIME[low.pow]);
  low.pow.ambi.temp = c(low.pow.temp, data$AMBIENT_TEMPERATURE[low.pow]);
  low.pow.mod.temp = c(low.pow.temp, data$MODULE_TEMPERATURE[low.pow]);
  low.pow.day = c(low.pow.day, data$DAY[low.pow])
  low.pow.irradiation = c(low.pow.irradiation, data$IRRADIATION[low.pow])
  
  

  
}
  hist(p1.f$numfail[p1.f$numfail!=0],seq(0,25,1),main="Histogram of Number of Simultanious Low Power Inverters")
  hist(data$AMBIENT_TEMPERATURE)
  hist(low.pow.ambi.temp, main="Histogram of AMBIENT_TEMPERATURE during low power")
  hist(data$MODULE_TEMPERATURE)
  hist(low.pow.mod.temp, main="Histogram of MODULE_TEMPERATURE during low power")
  hist(low.pow.day,main = "Histogram of Days where a Low Power Occured", breaks = 1:36);
  hist(data$TIME[low.pow])
  hist(low.pow.time,main = "Histogram of Times when a Low Power Occured", breaks = seq(min(data$TIME),max(data$TIME),15));
  hist(low.pow.irradiation,main = "Histogram of Irradiation when a Low Power Occured");
  
  # entries when there were more than 5 low power inverters at one time
  p1.f[p1.f$numfail>5,c(29:50)]
  
  fail.matrix = p1.f[p1.f$numfail>1,29:50]
  fail.pairs = NULL
  count = 0;
  for (i in 1:21){
    for (j in (i+1):22){
      count = count +1;
      fail.pairs$letter1[count] <- LETTERS[i];
      fail.pairs$letter2[count] <- LETTERS[j];
      fail.pairs$cofail[count] <- length(fail.matrix[fail.matrix[,i]+fail.matrix[,j] == 2,1]);
      
      }
  }
  fail.pairs=data.frame(fail.pairs)
  hist(fail.pairs$cofail,main = "Histogram of Inverter Pairs Experiencing Low Power Simultaniously")
  
  
  p = sum(p1.f$numfail)/length(p1gen$IRRADIATION[p1gen$IRRADIATION>0.4])
  pbinom(10,choose(22,2),prob = p)
  
  #correlation of fail matrix
  cor(fail.matrix, y=fail.matrix, use="all.obs")


```





```{r lower power lag 1 & 2 graphs}

# plots low power points, and the two data points temporally preceding the low power point.
# # green squares are two lags behind, orange triangles are one lag behind.

# it appears that low power moments are not preceded by low power moments.

for (i in 1:22){
  
  data = p1gen[p1gen$SOURCE==LETTERS[i],];
  z.pow = data$DC_POWER==0;
  mod=lm(DC_POWER~poly(IRRADIATION,2)+AMBIENT_TEMPERATURE,data=data[!z.pow,]);
  variance = var(data$DC_POWER[!z.pow]-predict(mod,data[!z.pow,]));
  sd = sqrt(variance);
  
  
  
  low.pow = !z.pow & data$DC_POWER < (predict(mod,data)-3*sd)
  lag1 = NULL;
  lag2 = NULL;
  lag.count = 0;
  
  for (j in 3:length(z.pow)){
    
    if(low.pow[j] & !z.pow[j-1] & !z.pow[j-2]){
      lag.count = lag.count+1;
      lag1[lag.count] = j-1;
      lag2[lag.count] = j-2;
    }
    
    
  }
  
  
  
  
  plot(data$IRRADIATION,data$DC_POWER,main = paste("low power time with lag 1 & 2 for SOURCE" ,LETTERS[i]), xlab = 
         "Irradiation", ylab = "Direct Current Power");
  points(data$IRRADIATION,predict(mod,data),col="blue",pch=20)
  points(data$IRRADIATION[low.pow],data$DC_POWER[low.pow],col="red",pch=20)
  points(data$IRRADIATION[lag1],data$DC_POWER[lag1],col="orange",pch=2)
  points(data$IRRADIATION[lag2],data$DC_POWER[lag2],col="green",pch=22)
  
  
  
}

```



```{r lower power lag 1 & 2 graphs}

# another visualization of low power points, plotting only residuals

for (i in 3:3){
  
  data = p1gen[p1gen$SOURCE==LETTERS[i],];
  z.pow = data$DC_POWER==0;
  mod=lm(DC_POWER~poly(IRRADIATION,2),data=data[!z.pow,]);
  variance = var(data$DC_POWER[!z.pow]-predict(mod,data[!z.pow,]));
  sd = sqrt(variance);
  
  
  
  low.pow = !z.pow & data$DC_POWER < (predict(mod,data)-3*sd)
  lag1 = NULL;
  lag2 = NULL;
  lag.count = 0;
  
  for (j in 3:length(z.pow)){
    
    if(low.pow[j] & !z.pow[j-1] & !z.pow[j-2]){
      lag.count = lag.count+1;
      lag1[lag.count] = j-1;
      lag2[lag.count] = j-2;
    }
    
    
  }
  
  
  residules = data$DC_POWER-predict(mod,data)
  
  plot(data$IRRADIATION,residules,main = paste("Residuals and Low Power Points for SOURCE" ,LETTERS[i]), xlab = 
         "Irradiation", ylab = "Direct Current Power");
  points(data$IRRADIATION,residules,col="blue",pch=20)
  points(data$IRRADIATION[low.pow],residules[low.pow],col="red",pch=20)
  points(data$IRRADIATION[lag1],residules[lag1],col="orange",pch=2)
  points(data$IRRADIATION[lag2],residules[lag2],col="green",pch=22)
  
  
  
}

```


```{r lower power fitting}

# Attempt to predict a low power moment based on five lag data points. Use Logistic Regression, LDA, QDA, and KNN. No method is effective.
# Results suggests that low power cannot be predicted from previous yield data.

library(MASS)
for (i in 3:3){
  
  data = p1gen[p1gen$SOURCE==LETTERS[i],];
  z.pow = data$DC_POWER==0;
  mod=lm(DC_POWER~poly(IRRADIATION,2),data=data[!z.pow,]);
  residuals = data$DC_POWER-predict(mod,data);
  data$lag1 = c(0,residuals[1:(length(data$DC_POWER)-1)]);
  data$lag2 = c(0,0,residuals[1:(length(data$DC_POWER)-2)]);
  data$lag3 = c(0,0,0,residuals[1:(length(data$DC_POWER)-3)]);
  data$lag4 = c(0,0,0,0,residuals[1:(length(data$DC_POWER)-4)]);
  data$lag5 = c(0,0,0,0,0,residuals[1:(length(data$DC_POWER)-5)]);

  
  plot(data$IRRADIATION,data$lag1)
  
  variance = var(data$DC_POWER[!z.pow]-predict(mod,data[!z.pow,]));
  sd = sqrt(variance);
  low.pow = !z.pow & data$DC_POWER < (predict(mod,data)-3*sd) & data$DC_POWER > (predict(mod,data)-7*sd)
  is.low = rep("NO",length(data$AC_POWER));
  is.low[low.pow]="YES"
  data$islow <- as.factor(is.low)
  

    
}
  glm.fits=glm(islow~lag1+lag2+lag3+lag4+lag5+poly(IRRADIATION,2),
             data=data[data$DC_POWER !=0,],family=binomial);
  glm.probs=predict(glm.fits,type="response")
  glm.pred=rep("NO",length(data$DC_POWER))
  glm.pred[glm.probs>.5]="YES"
  table(glm.pred,data$islow)
  mean(glm.pred==data$islow)
  plot(data$IRRADIATION,data$DC_POWER,main = paste("Logistic Regression Classification of LOW_POW in SOURCE" 
    ,LETTERS[i]), xlab = "Irradiation", ylab = "Direct Current Power");
  points(data$IRRADIATION,predict(mod,data),col="blue",pch=20)
  points(data$IRRADIATION[glm.pred=="YES"],data$DC_POWER[glm.pred=="YES"],col="red",pch=20)
  
  lda.fit=lda(islow~lag1+lag2+lag5+poly(IRRADIATION,2),data=data[data$DC_POWER !=0,])
  lda.pred=predict(lda.fit,data)
  table(lda.pred$class,data$islow)
  mean(lda.pred$class==data$islow)
  plot(data$IRRADIATION,data$DC_POWER,main = paste("lda Classificaiton of LOW_POW in SOURCE" ,LETTERS[i]), xlab = 
         "Irradiation", ylab = "Direct Current Power");
  points(data$IRRADIATION,predict(mod,data),col="blue",pch=20)
  points(data$IRRADIATION[lda.pred$class=="YES"],data$DC_POWER[lda.pred$class=="YES"],col="red",pch=20)
  
  qda.fit=qda(islow~lag1+lag2+lag5+poly(IRRADIATION,2),data=data[data$DC_POWER !=0,])
  qda.pred=predict(qda.fit,data)
  table(qda.pred$class,data$islow)
  mean(qda.pred$class==data$islow)
  plot(data$IRRADIATION,data$DC_POWER,main = paste("qda Classification of LOW_POW in SOURCE" ,LETTERS[i]), xlab = 
         "Irradiation", ylab = "Direct Current Power");
  points(data$IRRADIATION,predict(mod,data),col="blue",pch=20)
  points(data$IRRADIATION[qda.pred$class=="YES"],data$DC_POWER[qda.pred$class=="YES"],col="red",pch=20)
  
  
library(class)
set.seed(1)
data=data[data$DC_POWER !=0,]
knn.pred=knn(data[,10:15],data[,10:15],data$islow,k=3)
  table(knn.pred,data$islow)
  mean(knn.pred==data$islow)
  plot(data$IRRADIATION,data$DC_POWER,main = paste("knn, k=3 Classification of LOW_POW in SOURCE" ,LETTERS[i]), xlab = 
         "Irradiation", ylab = "Direct Current Power");
  points(data$IRRADIATION,predict(mod,data),col="blue",pch=20)
  points(data$IRRADIATION[knn.pred=="YES"],data$DC_POWER[knn.pred=="YES"],col="red",pch=20)
table(knn.pred,data$islow)
mean(knn.pred==data$islow)
  


  

  
  
  

```


