---
title: "Powerplant Analysis"
author: "Daniel Lundstrom"
output:
  word_document: default
  html_document: default
  pdf_document: default
---


Here we attempt to predict power output vs available predictors. We find that
AC_POWER is a linear multiple of DC_POWER. As such, only fit on dc power readings
or the total plant yield.

We find that irradiation is the fundamental predictor of yield, but ambient
temperature is correlated with the aspects of the power yield, such as variance.
We try polynomial, ridge, lasso, and spline fittings, and find that higher power
fittings regularized methods and splines do not improve greatly on the quadratic
fitting.


```{r dc vs ac power}
#AC_POWR and DC_POWER are essentially linearly related. It would be easy to
# construct a test to see if there is power leakage in the conversion.

plot(p1gen$AC_POWER,p1gen$DC_POWER)

```




```{r fitting_dcp}

# Creates plots of irradiation vs power output for different inverters.
# Try linear and quadratic fits and compare R^2 values.

RSS.lm1 = NULL;
RSS.lm2 = NULL;
TSS = NULL;
r2.lm1 = NULL;
r2.lm2 = NULL
coeff.lm = NULL;

for (i in 1:22){
  plot(p1$IRRADIATION,p1[,i+5]);
  
  lm.fit=lm(p1[,i+5]~IRRADIATION+AMBIENT_TEMPERATURE,data=p1);
  RSS.lm1[i] = mean((p1[,i+5]-predict(lm.fit,p1))^2);
  points(p1$IRRADIATION,predict(lm.fit,p1),col="red")
  
  lm.fit=lm(p1[,i+5]~poly(IRRADIATION,2)+AMBIENT_TEMPERATURE,data=p1);
  RSS.lm2[i] = mean((p1[,i+5]-predict(lm.fit,p1))^2);
  points(p1$IRRADIATION,predict(lm.fit,p1),col="blue")
  
  TSS[i] = mean((p1[,i+5]-mean(p1[,i+5]))^2);
  r2.lm1[i] = 1-RSS.lm1[i]/TSS[i];
  r2.lm2[i] = 1-RSS.lm2[i]/TSS[i];
}

r2.lm2-r2.lm1

# Try linear fit using all data from other power inverters (blue).

for (i in 1:22){
  plot(p1$IRRADIATION,p1[,i+5]);
  
  lm.fit=lm(p1[,i+5]~IRRADIATION+AMBIENT_TEMPERATURE,data=p1);
  RSS.lm1[i] = mean((p1[,i+5]-predict(lm.fit,p1))^2);
  points(p1$IRRADIATION,predict(lm.fit,p1),col="red")
  
  lm.fit=lm(as.formula(paste(colnames(p1)[i+5],"~.")),data=p1);
  RSS.lm2[i] = mean((p1[,i+5]-predict(lm.fit,p1))^2);
  points(p1$IRRADIATION,predict(lm.fit,p1),col="blue")
  
  TSS[i] = mean((p1[,i+5]-mean(p1[,i+5]))^2);
  r2.lm1[i] = 1-RSS.lm1[i]/TSS[i];
  r2.lm2[i] = 1-RSS.lm2[i]/TSS[i];
}

#using all other inverters raises R^2 significantly compared to quadratic fitting.
r2.lm2-r2.lm1




# illustrates that different inverters have different irradiation vs power curves.

plot(p1$IRRADIATION, p1$Edcp, col="orange")
points(p1$IRRADIATION, p1$Fdcp, col="black")


```

```{r 2nd degree fits with different predictors}
# Investigation of relevant predictors to power output.
# Irradiation and ambient temp seem to be the only relevant predictors

RSS.mod1 = NULL;
RSS.mod2 = NULL;
RSS.mod3 = NULL;
RSS.mod4 = NULL;
RSS.lmod1 = NULL;
RSS.lmod2 = NULL;
RSS.lmod3 = NULL;
RSS.lmod4 = NULL;
TSS = NULL;
r2.lm1 = NULL;
r2.lm2 = NULL;
r2.lm3 = NULL;
r2.lm4 = NULL;
r2.llm1 = NULL;
r2.llm2 = NULL;
r2.llm3 = NULL;
r2.llm4 = NULL;

coeff.lm = NULL;

for (i in 1:22){
  
  x1 = model.matrix(as.formula(paste(colnames(p1nz)[i+5],"~poly(IRRADIATION,2)")),p1nz)[,-1];
  y1 = p1nz[,i+5];
  mod.fit1=cv.glmnet(x1,y1,type.measure = "mse",alpha=1);
  RSS.lmod1[i] = mean((p1nz[,i+5]-predict(mod.fit1,s=mod.fit1$lambda.min,newx=x1))^2);
  
  x1 = model.matrix(as.formula(paste(colnames(p1nz)[i+5],"~poly(IRRADIATION,2)+AMBIENT_TEMPERATURE")),p1nz)[,-1];
  y1 = p1nz[,i+5];
  mod.fit1=cv.glmnet(x1,y1,type.measure = "mse",alpha=1);
  RSS.lmod2[i] = mean((p1nz[,i+5]-predict(mod.fit1,s=mod.fit1$lambda.min,newx=x1))^2);
  
  x1 = model.matrix(as.formula(paste(colnames(p1nz)[i+5],"~poly(IRRADIATION,2)+MODULE_TEMPERATURE")),p1nz)[,-1];
  y1 = p1nz[,i+5];
  mod.fit1=cv.glmnet(x1,y1,type.measure = "mse",alpha=1);
  RSS.lmod3[i] = mean((p1nz[,i+5]-predict(mod.fit1,s=mod.fit1$lambda.min,newx=x1))^2);
  
  x1 = model.matrix(as.formula(paste(colnames(p1nz)[i+5],"~poly(IRRADIATION,2)+AMBIENT_TEMPERATURE+MODULE_TEMPERATURE")),p1nz)[,-1];
  y1 = p1nz[,i+5];
  mod.fit1=cv.glmnet(x1,y1,type.measure = "mse",alpha=1);
  RSS.lmod4[i] = mean((p1nz[,i+5]-predict(mod.fit1,s=mod.fit1$lambda.min,newx=x1))^2);
  
  
  mod.fit1=lm(p1nz[,i+5]~poly(IRRADIATION,2),data=p1nz);
  RSS.mod1[i] = mean((p1nz[,i+5]-predict(mod.fit1,p1nz))^2);
  
  mod.fit2=lm(p1nz[,i+5]~poly(IRRADIATION,2)+AMBIENT_TEMPERATURE,data=p1nz);
  RSS.mod2[i] = mean((p1nz[,i+5]-predict(mod.fit2,p1nz))^2);
  
  mod.fit3=lm(p1nz[,i+5]~poly(IRRADIATION,2)+MODULE_TEMPERATURE,data=p1nz);
  RSS.mod3[i] = mean((p1nz[,i+5]-predict(mod.fit3,p1nz))^2);
  
  mod.fit4=lm(p1nz[,i+5]~poly(IRRADIATION,2)+MODULE_TEMPERATURE+AMBIENT_TEMPERATURE,data=p1nz);
  RSS.mod4[i] = mean((p1nz[,i+5]-predict(mod.fit4,p1nz))^2);
  
  
  TSS[i] = mean((p1nz[,i+5]-mean(p1nz[,i+5]))^2);
  r2.lm1[i] = 1-RSS.mod1[i]/TSS[i];
  r2.lm2[i] = 1-RSS.mod2[i]/TSS[i];
  r2.lm3[i] = 1-RSS.mod3[i]/TSS[i];
  r2.lm4[i] = 1-RSS.mod4[i]/TSS[i];
  r2.llm1[i] = 1-RSS.lmod1[i]/TSS[i];
  r2.llm2[i] = 1-RSS.lmod2[i]/TSS[i];
  r2.llm3[i] = 1-RSS.lmod3[i]/TSS[i];
  r2.llm4[i] = 1-RSS.lmod4[i]/TSS[i];
  

}

mean(r2.lm1)
mean(r2.lm2)
mean(r2.lm3)
mean(r2.lm4)
mean(r2.llm1)
mean(r2.llm2)
mean(r2.llm3)
mean(r2.llm4)


```


```{r spline fitting}

library(splines);
RSS.mod1 = NULL;
RSS.mod2 = NULL;
RSS.mod3 = NULL;
TSS = NULL;
r2.spline1 = NULL;
r2.spline2 = NULL;
r2.spline3 = NULL;


num.plots = 1;

IRRlims = range(p1nz$IRRADIATION);
IRR.grid = seq(from=IRRlims[1],to=IRRlims[2]);


for (i in 1:1){

  mod.fit1=lm(as.formula(paste(colnames(p1nz)[i+5],"~bs(IRRADIATION,knots=c(0.4,0.8))")),data=p1nz);
  list(IRRADIATION = IRR.grid)
  pred1 = predict(mod.fit1,newdata=list(IRRADIATION=p1nz$IRRADIATION),se=T);
  RSS.mod1[i] = mean((p1nz[,i+5]-pred1$fit)^2);
  
  mod.fit2=lm(as.formula(paste(colnames(p1nz)[i+5],"~bs(IRRADIATION,knots=c(0.4,0.6,0.8))")),data=p1nz);
  list(IRRADIATION = IRR.grid)
  pred2 = predict(mod.fit2,newdata=list(IRRADIATION=p1nz$IRRADIATION),se=T);
  RSS.mod2[i] = mean((p1nz[,i+5]-pred2$fit)^2);
  
  mod.fit3=lm(as.formula(paste(colnames(p1nz)[i+5],"~bs(IRRADIATION,knots=c(0.4,0.6,0.8,1))")),data=p1nz);
  list(IRRADIATION = IRR.grid)
  pred3 = predict(mod.fit3,newdata=list(IRRADIATION=p1nz$IRRADIATION),se=T);
  RSS.mod3[i] = mean((p1nz[,i+5]-pred3$fit)^2);

  TSS[i] = mean((p1nz[,i+5]-mean(p1nz[,i+5]))^2);
  r2.spline1[i] = 1-RSS.mod1[i]/TSS[i];
  r2.spline2[i] = 1-RSS.mod2[i]/TSS[i];
  r2.spline3[i] = 1-RSS.mod3[i]/TSS[i];
  
  if (i <= num.plots){
    plot(p1nz$IRRADIATION,p1nz[,i+5],main = paste("Ridge Regression Fits of",colnames(p1nz)[i+5], "with polynomial Irradiation"),     xlab = "Irradiation", ylab = "Direct Current Power");
    points(p1nz$IRRADIATION,pred1$fit,col="red",pch=20)
    points(p1nz$IRRADIATION,pred2$fit,col="blue",pch=20)
    points(p1nz$IRRADIATION,pred3$fit,col="green",pch=20)
    
  }
}

mean(r2.spline1);
mean(r2.spline2);
mean(r2.spline3);

var(r2.spline3)
```



```{r lasso fitting}

library(glmnet);
RSS.mod1 = NULL;
RSS.mod2 = NULL;
RSS.mod3 = NULL;
TSS = NULL;
r2.lasso1 = NULL;
r2.lasso2 = NULL;
r2.lasso3 = NULL;

coeff.lm = NULL;
num.plots =2;

for (i in 1:22){
  
  #plot(p1nz$IRRADIATION,p1nz[,i+5],main = paste("Ridge Regression Fits of",colnames(p1nz)[i+5], "with polynomial Irradiation"),     xlab = "Irradiation", ylab = "Direct Current Power");
  
  x1 = model.matrix(as.formula(paste(colnames(p1nz)[i+5],"~poly(IRRADIATION,1)+AMBIENT_TEMPERATURE")),p1nz)[,-1];
  y1 = p1nz[,i+5];
  mod.fit1=cv.glmnet(x1,y1,type.measure = "mse",alpha=1);
  RSS.mod1[i] = mean((p1nz[,i+5]-predict(mod.fit1,s=mod.fit1$lambda.min,newx=x1))^2);
  #points(p1nz$IRRADIATION,predict(mod.fit1,s=mod.fit1$lambda.min,newx=x1),col="red",pch=20)
  
  x2 = model.matrix(as.formula(paste(colnames(p1nz)[i+5],"~poly(IRRADIATION,2)+AMBIENT_TEMPERATURE")),p1nz)[,-1];
  y2 = p1nz[,i+5];
  mod.fit2=cv.glmnet(x2,y2,type.measure = "mse",alpha=1);
  RSS.mod2[i] = mean((p1nz[,i+5]-predict(mod.fit2,s=mod.fit2$lambda.min,newx=x2))^2);
  #points(p1nz$IRRADIATION,predict(mod.fit2,s=mod.fit2$lambda.min,newx=x2),col="blue",pch=20)
  
  x3 = model.matrix(as.formula(paste(colnames(p1nz)[i+5],"~poly(IRRADIATION,3)+AMBIENT_TEMPERATURE")),p1nz)[,-1];
  y3 = p1nz[,i+5];
  mod.fit3=cv.glmnet(x3,y3,type.measure = "mse",alpha=1);
  RSS.mod3[i] = mean((p1nz[,i+5]-predict(mod.fit3,s=mod.fit3$lambda.min,newx=x3))^2);
  #points(p1nz$IRRADIATION,predict(mod.fit3,s=mod.fit3$lambda.min,newx=x3),col="green",pch=20)
  
  
  TSS[i] = mean((p1nz[,i+5]-mean(p1nz[,i+5]))^2);
  r2.lasso1[i] = 1-RSS.mod1[i]/TSS[i];
  r2.lasso2[i] = 1-RSS.mod2[i]/TSS[i];
  r2.lasso3[i] = 1-RSS.mod3[i]/TSS[i];
  
  if (i <= num.plots){
    plot(p1nz$IRRADIATION,p1nz[,i+5],main = paste("Lasso Regression Fits of",colnames(p1nz)[i+5], "with polynomial Irradiation"),     xlab = "Irradiation", ylab = "Direct Current Power");
  points(p1nz$IRRADIATION,predict(mod.fit1,s=mod.fit1$lambda.min,newx=x1),col="red",pch=20)
  points(p1nz$IRRADIATION,predict(mod.fit2,s=mod.fit2$lambda.min,newx=x2),col="blue",pch=20)
  #points(p1nz$IRRADIATION,predict(mod.fit3,s=mod.fit3$lambda.min,newx=x3),col="green",pch=20)
  }
  
}
  #third degree hugs pretty well
  plot(p1nz$IRRADIATION,p1nz[,i+5],main = paste("Lasso Regression Fits of",colnames(p1nz)[i+5], "with polynomial Irradiation"),     xlab = "Irradiation", ylab = "Direct Current Power");
  points(p1nz$IRRADIATION,predict(mod.fit3,s=mod.fit3$lambda.min,newx=x3),col="green",pch=20)

mean(r2.lasso1)
mean(r2.lasso2)
mean(r2.lasso3)

var(r2.lasso3)


```

```{r ridge fitting}
library(glmnet);
RSS.mod1 = NULL;
RSS.mod2 = NULL;
RSS.mod3 = NULL;
TSS = NULL;
r2.ridge1 = NULL;
r2.ridge2 = NULL;
r2.ridge3 = NULL;

coeff.lm = NULL;

num.plots = 2;

for (i in 1:1){
  
  #plot(p1nz$IRRADIATION,p1nz[,i+5],main = paste("Ridge Regression Fits of",colnames(p1nz)[i+5], "with polynomial Irradiation"),     xlab = "Irradiation", ylab = "Direct Current Power");
  
  x1 = model.matrix(as.formula(paste(colnames(p1nz)[i+5],"~poly(IRRADIATION,1)+AMBIENT_TEMPERATURE")),p1nz)[,-1];
  y1 = p1nz[,i+5];
  mod.fit1=cv.glmnet(x1,y1,type.measure = "mse",alpha=0);
  RSS.mod1[i] = mean((p1nz[,i+5]-predict(mod.fit1,s=mod.fit1$lambda.min,newx=x1))^2);
  #points(p1nz$IRRADIATION,predict(mod.fit1,s=mod.fit1$lambda.min,newx=x1),col="red",pch=20)
  
  x2 = model.matrix(as.formula(paste(colnames(p1nz)[i+5],"~poly(IRRADIATION,2)+AMBIENT_TEMPERATURE")),p1nz)[,-1];
  y2 = p1nz[,i+5];
  mod.fit2=cv.glmnet(x2,y2,type.measure = "mse",alpha=0);
  RSS.mod2[i] = mean((p1nz[,i+5]-predict(mod.fit2,s=mod.fit2$lambda.min,newx=x2))^2);
  #points(p1nz$IRRADIATION,predict(mod.fit2,s=mod.fit2$lambda.min,newx=x2),col="blue",pch=20)
  
  x3 = model.matrix(as.formula(paste(colnames(p1nz)[i+5],"~poly(IRRADIATION,3)+AMBIENT_TEMPERATURE")),p1nz)[,-1];
  y3 = p1nz[,i+5];
  mod.fit3=cv.glmnet(x3,y3,type.measure = "mse",alpha=0);
  RSS.mod3[i] = mean((p1nz[,i+5]-predict(mod.fit3,s=mod.fit3$lambda.min,newx=x3))^2);
  #points(p1nz$IRRADIATION,predict(mod.fit3,s=mod.fit3$lambda.min,newx=x3),col="green",pch=20)
  
  
  TSS[i] = mean((p1nz[,i+5]-mean(p1nz[,i+5]))^2);
  r2.ridge1[i] = 1-RSS.mod1[i]/TSS[i];
  r2.ridge2[i] = 1-RSS.mod2[i]/TSS[i];
  r2.ridge3[i] = 1-RSS.mod3[i]/TSS[i];
  
  if (i<= num.plots){
    plot(p1nz$IRRADIATION,p1nz[,i+5],main = paste("Ridge Regression Fits of",colnames(p1nz)[i+5], "with polynomial    
        Irradiation"),     xlab = "Irradiation", ylab = "Direct Current Power");
    points(p1nz$IRRADIATION,predict(mod.fit1,s=mod.fit1$lambda.min,newx=x1),col="red",pch=20)
    points(p1nz$IRRADIATION,predict(mod.fit2,s=mod.fit2$lambda.min,newx=x2),col="blue",pch=20)
    points(p1nz$IRRADIATION,predict(mod.fit3,s=mod.fit3$lambda.min,newx=x3),col="green",pch=20)
  }
  
}

mean(r2.ridge1)
mean(r2.ridge2)
mean(r2.ridge3)

var(r2.ridge3)


```


```{r illustrations}

#illustrates that higher temperatures cause an increase in variance.

plot(p1$IRRADIATION[p1$AMBIENT_TEMPERATURE>28], p1$Adcp[p1$AMBIENT_TEMPERATURE>28],col="red")
points(p1$IRRADIATION[p1$AMBIENT_TEMPERATURE<28], p1$Adcp[p1$AMBIENT_TEMPERATURE<28],col="blue")

plot(p1gen$IRRADIATION[p1gen$AMBIENT_TEMPERATURE>29], p1gen$DC_POWER[p1gen$AMBIENT_TEMPERATURE>29],col="red")
points(p1gen$IRRADIATION[p1gen$AMBIENT_TEMPERATURE<29], p1gen$DC_POWER[p1gen$AMBIENT_TEMPERATURE<29],col="blue")


```




```{r bag_of_holding}
#plot(p1gen$IRRADIATION[p1gen$SOURCE == "A"], p1gen$DC_POWER[p1gen$SOURCE == "A"],col="blue")

#points(p1gen$IRRADIATION[p1gen$SOURCE == "B"], p1gen$DC_POWER[p1gen$SOURCE == "B"],col="red")

#points(p1gen$IRRADIATION[p1gen$SOURCE == "C"], p1gen$DC_POWER[p1gen$SOURCE == "C"], col="green")
#points(p1gen$IRRADIATION[p1gen$SOURCE == "D"], p1gen$DC_POWER[p1gen$SOURCE == "D"], col="purple")

#points(p1gen$IRRADIATION[p1gen$SOURCE == "E"], p1gen$DC_POWER[p1gen$SOURCE == "E"], col="black")

#points(p1gen$IRRADIATION[p1gen$SOURCE == "F"], p1gen$DC_POWER[p1gen$SOURCE == "F"], col="orange")

#plot(p1sen$TIME[p1sen$DAY == 1], p1sen$IRRADIATION[p1sen$DAY == 1],col="red")
#plot(p1sen$TIME[p1sen$DAY == 2], p1sen$IRRADIATION[p1sen$DAY == 2],col="red")
#plot(p1sen$TIME[p1sen$DAY == 3], p1sen$IRRADIATION[p1sen$DAY == 3],col="red")
#plot(p1sen$TIME[p1sen$DAY == 4], p1sen$IRRADIATION[p1sen$DAY == 4],col="red")




#plot(p1gen$IRRADIATION, p1gen$DC_POWER)
#n=28
#plot(p1gen$IRRADIATION[p1gen$AMBIENT_TEMPERATURE>n], p1gen$DC_POWER[p1gen$AMBIENT_TEMPERATURE>n],col="red")
#length(p1gen$IRRADIATION[p1gen$AMBIENT_TEMPERATURE>n])
#points(p1gen$IRRADIATION[p1gen$AMBIENT_TEMPERATURE<n], p1gen$DC_POWER[p1gen$AMBIENT_TEMPERATURE<n],col="blue")
#length(p1gen$IRRADIATION[p1gen$AMBIENT_TEMPERATURE<n])

```

